Default GMSE data structures

### 2020-05-22 notebook/ms/SI7.Rmd
Started working on some extra text in SI7 for ownership_var, examples to follow

Events in default GMSE sub-models occur on a spatially-explicit landscape `LAND`, which is stored as a three dimensional array. The size of this landscape is specified with the `land_dim_1` and `land_dim_2` arguments of GMSE, which determine the length, in cells, of the y and x dimensions of the landscape, respectively (e.g., if `land_dim_1 = 10` and `land_dim_2 = 1000`, then the landscape will be one very long horizontal transect). The total number of landscape cells on which resources and agents can interact is therefore the product of `land_dim_1` and `land_dim_2`. In addition, all landscapes have three layers, which hold three separate values of information for each x-y location. The first layer is unused as of GMSE v0.4.0.7; the second layer holds crop production on a cell, and the third layer holds the owner of the cell (corresponding to the ID of an agent, where the manager's ID = 0 defines public land). An $8 \times 8$ portion of the landscape from `sim` is shown below.

@@

>>>>

Events in default GMSE sub-models occur on a spatially-explicit landscape `LAND`, which is stored as a three dimensional array. The size of this landscape is specified with the `land_dim_1` and `land_dim_2` arguments of GMSE, which determine the length, in cells, of the y and x dimensions of the landscape, respectively (e.g., if `land_dim_1 = 10` and `land_dim_2 = 1000`, then the landscape will be one very long horizontal transect). The total number of landscape cells on which resources and agents can interact is therefore the product of `land_dim_1` and `land_dim_2`. In addition, all landscapes have three layers, which hold three separate values of information for each x-y location. The first layer is unused as of GMSE v0.6.0.0; the second layer holds crop production on a cell, and the third layer holds the owner of the cell (corresponding to the ID of an agent, where the manager's ID = 0 defines public land). An $8 \times 8$ portion of the landscape from `sim` is shown below.

@@

In addition, whereas in previous versions variable landscape ownership among users had to be customised using `gmse_apply`, GMSE v. 0.6.0.0+ now includes an additional parameter `ownership_var`, which takes effect when `land_ownership = TRUE`. The value of this parameter is expected to be >=0 and <1. At its default value of 0, land ownership is equal among users as demonstrated in the code above. Values >0 increase the extent of variability of landownership among users.

*** Working on examples here ***
